---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  # collapse = TRUE,
  results = "asis",
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(tex2img)
# remotes::install_github("GuangchuangYu/badger")
library(badger)
```

# tex2img

<!-- badges: start -->
`r # badge_cran_release(color = "brightgreen")`
`r badge_lifecycle("experimental")`
`r badge_license(color = "blueviolet")`
`r # badge_github_actions(action = "R-CMD-check")`
`r # badge_codecov()`
`r # badge_dependencies()`
<!-- badges: end -->

Convert TeX equations to images using [Sciweavers iTex2Img](http://www.sciweavers.org/free-online-latex-equation-editor)

## Installation

<!-- You can install the released version of **tex2img** from [CRAN](https://cran.r-project.org/) with: -->

<!-- ```{r eval = FALSE} -->
<!-- install.packages("tex2img") -->
<!-- ``` -->

Or the development version of **tex2img** from [GitHub](https://github.com/rossellhayes/tex2img) with:

``` {r eval = FALSE}
install_github("rossellhayes/tex2img")
```

## Usage

**tex2img** allows TeX equations to be embedded in Markdown documents (like GitHub READMEs) as images.

```{r eval = FALSE}
`r tex2img("\\frac{22}{7}")`
```

`r tex2img("\\frac{22}{7}")`

A number of options are provided to fine tune the image.

```{r eval = FALSE}
`r tex2img(
  "\\frac{22}{7}", color = "ForestGreen", background = "RawSienna",
  font = "Modern", size = 18, type = "jpg"
)`
```

`r tex2img(
  "\\frac{22}{7}", color = "White", background = "PineGreen",
  font = "Modern", size = 18, type = "jpg"
)`

---

Please note that **tex2img** is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
